\chapter{Appendix}
\singlespacing
\section{Author/Editor Legend}
\begin{itemize}
    \item {\tt QH} -- Qingyang Hu
    \item {\tt JL} -- Jhan-Shuo (Jeff) Liu
    \item {\tt NK} -- Nozomu Kitamura
\end{itemize}
\section{Academic Integrity Pledge}
We affirm that we are the sole authors of this report and we give due credit (i.e., use correct citations) to all used sources.


\noindent\begin{tabular}{@{}p{2.5in}p{2.5in}@{}}
  \\[1\bigskipamount]
  {\cursive \Large Nozomu Kitamura} & {\cursive \Large 4/9/2024}\\
  \hrulefill & \hrulefill \\
  Author: Nozomu Kitamura & Date \\[2\bigskipamount]
   {\cursive \Large Qingyang Hu} & {\cursive \Large 4/9/2024}\\
  \hrulefill & \hrulefill \\
  Author: Qingyang Hu & Date \\[2\bigskipamount]
  {\cursive \Large Jhan-Shuo (Jeff) Liu} & {\cursive \Large 4/9/2024}\\
  \hrulefill & \hrulefill \\
  Author: Jhan-Shuo (Jeff) Liu & Date \\
\end{tabular}

\newpage
\doublespacing
\section{Turnitin Reflection}
The Turnitin score was 1\%\footnote{Note: We were not able to generate the similarity report using our PDF. However, a workaround by selecting and copying all texts into a TXT file has successfully allowed us to generate the similarity score. All scores here refer to the text version, which contains all the texts we have.}. We went through every match to ensure that it was superfluous.

The Introduction section contributes to the similarity score, although by less than 1\%. However, these relate to figures such as dollars and units, as well as terms such as ``compound annual growth rate (CAGR)'' for which we have already cited sources appropriately.

Finally, the minor matches in the literature review of Traffic congestion factors contribute to 1\% of the similarity score, although less than 1\% as well. However, these matches are matched to terms in the Traffic congestion factors, and we have properly cited our sources for this as well.
